
\indent \indent \textbf{Group communication} \\
The communication inside the team worked well, because we were working in the same room most of the time. This contributed to the prevention of conflicts. We also had some "Team building" that helped us not get on each others nerves. Other than that we used SMS to keep in contact with each other outside of the university. This resulted in quite a good team spirit and there were no major mishaps regarding communication inside the group.
\\

\textbf{Supervisor communication} \\
The overall communication with the supervisor has been as expected. Some times there would have been nice with an answer to some of the emails about meetings. Typically we ask the supervisor for a meeting, decide time and place, and the supervisor doesn't confirm the meeting time, but he shows up so there is not really a problem. Other than that we had a good rapport with the supervisor and he always answered our questions. He was particularly good at helping us with the report, guiding us on how to lay it out and explaining what a good report should contain. There was very easy dealing with him as we could just send him an email or even meet him at his office.

For the most part our meetings with him went quite well except for one little communication error which we did not present clear enough to him. In the start of the project we were not quite sure what development methodology we were going to use and as stated earlier we eventually went with a modified waterfall model. The supervisor recommended SCRUM and was quite supportive of that way of developing. The problem arose when we did not convey clearly to him that we had chosen waterfall and some of the meetings ended with some confusion because of this. But we took it up during a later meeting and straighten every thing out.

The biweekly meetings with the supervisor worked well and we could always count on some insight into the problems we had faced. We also received good feed back on the weekly reports, activity plans and schedules which we sent.
\\ 

\textbf{Customer communication} \\
Since the customer was located in Oslo we had quite a challenge when it came to communication. Early on we decided together with the customer that we wanted to do weekly meetings over Skype. This worked out very well and we got lots of feedback over Skype. The customer did not mind us sending a lot of emails either, meaning that a lot of communication went over email which worked out very well. We got feedback when we needed it and we resolved problems either over email or, if the subject needed some discussion, at the weekly meeting. The customer also gave us very good feedback on the report which indicated their level of commitment. 

In addition to all this they also made several trips to Trondheim where we would have face to face meetings. This worked quite well, but we did not always prepare the way we should or could and some of the meetings were quite short for a trip from Oslo to Trondheim. But this level of commitment from the customer really impressed us and we are quite grateful that they gave us this opportunity.
\\

