% the flat structure worked out well
% we had no conflicts in the group. 
% the task distribution that automatically happened 
% comment on how this worked: some people had the unofficial responsibility for some tasks. Jan - IS, Jørgen - NS3, Ola - rooms, Magnus - Report, Stig - client. 
% evaluate the work schedule - mon-thur/10-16.
The problem we had with the roles in the group is that we did not manage to change up the roles during the project. This has resulted in some instances where we could not proceed with something because someone was ill. This was something that we were quite wary of in the beginning of the project, but we did not follow it up with the same care. Some of the reason behind this is that is was sometimes just easier to ask the person in charge to tell you about the parts that you did not know about. Another reason was that we worked together every day during the project which probably gave us the false confidence that we would not need to share the information. The few early roadblocks that we did encounter during the start up when we could have done something about it were probably so small that we just carried on without thinking about it.

We feel that the flat structure we chose worked out quite nice. When we came to a big decision that one of us felt uneasy about taking full responsibility for we talked about it in the group and would come up with a group decision. There are many reasons why this worked in our group, but a key enabler was the fact that we worked together Monday to Thursday. This close proximity made such decisions easy to approach and agreement could quickly be made. If we had not had this work schedule this sort of management might not have worked out the way it did.

We mentioned roles above, the fact that we did not change roles during the project, but we would also like to mention a bit about how that worked in the day to day. Because we grew into certain roles as the project progressed we also got some responsibilities. For instance Magnus quickly became the main contact between the group and the supervisor, but having only one person there did not hinder use. In fact the communication became quicker, because the supervisor could relate to one person and not everyone and the fact that when someone in the group wanted to ask the superviso about something they could contact Magnus.

Luckily we had very few conflicts in the group, there were some miscommunication which led to some disagreements, but there where very few of these. Among the few things that came up during this 15 week long project was a miscommunication about when we would start working again after the Easter vacation. This little incident only lead to some stressful days and the misunderstanding was cleared away.

As mentioned above we tried to work together Monday to Thursday from 10:00 to 16:00. This worked rather well during the whole project except for some hiccups regarding the "early" start. We had some weeks where not all of us were managed to get up in time, but after a meeting within the group we cleared away any bad air and did not really experience any such hiccups after that.
