% was the task well enough described? Or would it have been better if the task was stricter and had more requirements?
Our task was very focused on research, and with that came a lot of freedom to choose which technologies to use, and to some degree what to actually implement. We did manage to settle on some requirements quite early, although most of them were not very strict. Even so, we felt this was not a problem and started designing, but in the later parts of the project we realized having such loose requirements might have led us to grasp over a bit much. Stricter prioritized requirements might have let us know what parts were more important than others, and we could have focused more on them. We realize we should have asked the customer for these stricter requirements on both what to use and what to implement.

Since the project was research focused from the customer side we got quite a lot of freedom when it came to the project. This freedom was not a hindrance for us, but we could have handled it better. As mentioned above the requirements we agreed on with the customer was a bit to loose, again here we should have realized that they gave us this freedom and we should have insisted on stricter requirements. When it came to testing the customer gave us the same freedom and again we should have used that freedom to write up some strict test requirements. In the end the freedom gave us all the choices, but we could have handled it better.

Overall, the task has been very interesting, and we are in general very happy with the result of it.
