All in all the project has been very interesting. We have had some great experiences and we are left with a much better understanding of what it takes to create a complex system of interacting parts.

We have learned a lot about staying in contact with a customer and have a new understanding of what it takes to communicate with an outside entity which may or may not have the same idea as you. For this project the customer was very helpful in every way, but we also understood the importance of an open dialog where nothing is hidden.

During early development we took activity plans quite lightly which is something that we realized later that we should not. The importance of clear prioritizes and things to do became quite obvious to us. We also fumbled a bit at the end with activity plans which could account for our slow progress at the end.

We had few problems within the group, but we quickly understood the importance of clear communication which is something that we definitely could get better next time.

We have also learned that using libraries and frameworks that other people have made can be both a blessing and a curse. As we have documented there has at least been two occasions where we had to abandon frameworks and libraries which were not well documented and also opposed to large of a performance impact. For future works consulting with more experienced persons would be very beneficial and should that not work at least have an understanding with the customer that this could become a problem later.
