\subsection{Future Work}\label{Future Work}
    In this section we will discuss what can be worked on, and further improved in the future. Some things we did not have time to do, as well as some improvements we might have wanted, and some things that we knew would have to be made or modified later.

    \subsubsection{Server}\label{Future:Server}
        In our MS Mediator, we use a dummy implementation of the MS Communicator, which just reads an XML-file with the needed data. Making an implementation that actually contacts a Monitoring Service, and use this in the mediator, is something that should be implemented in the future.

        The throttling done in the ESB is relatively static, one configuration will work very well for some scenarios, but might not work as well for other ones. In the future, making it more dynamic might be desirable. The "Timeout" used in the ESB could be made dynamic by monitoring how long messages need to send to each endpoint and then varying the timeout after this. The message size should also be monitored so it could be used to decide when to preempt. Another thing to do might be to make and use a new implementation of the Message Processor instead of the built in SamplingMessageProcessor, retrieving a message from the Prioritized Message Store dynamically instead of just once every predefined interval milliseconds could get you a long way. Also the Throttle mediator could be made more dynamic, for example by varying the now static variables based on perceived network load. The preempting can also be improved greatly by taking into account how long a message has been sent and which priority it has 
gotten.

        If proper SAML authentication is implemented, the IdentityServer proxy sequence would have to be modified as well.

	\subsubsection{Client}\label{Future:Client}
		As mentioned in section~\ref{Changes}~changes, the components related to authentication on the client side were not implemented as desired due to the problems with the Identity Server. Naturally, this is an issue that should be adressed when a proper IS is present.

		The use of HTTPS, which is a result of our wish to use the Identity Server, could also be made more modular. During our testing we did experience some problems with SSL handshaking having timeouts. This should not be big problems as that would almost guarantee that our messages during testing would also timeout.
		
    	Other than that there is little unfinished tasks in the client library. However, there could always be better and more unit tests. 

