\section{File Attachments}\label{File Attachments} 
    % TODO: fix zip ang gitpath. 
    Files are found in: fileAttachments.zip \\
    Or at: https://github.com/magnuskiro/it2901/ path/to/raw/file
    
\begin{itemize}

    \begin{file}
        \label{attachment:file:QoS-Introduction}
        \item bachelor-QoS.pdf
        \subitem Introduction to the assignment and Quality of Service(QoS) support for Web services in military networks.
    \end{file}

    \begin{file}
        \label{attachment:file:Risk List}
        \item risklist.pdf 
        \subitem The full risk list attached in its full glory.
    \end{file}
    
    \begin{file}
        \label{attachment:file:Gantt}
        \item gantt.html
        \subitem Our gantt chart in its full form.
    \end{file}
    
    \begin{file}
        \label{attachment:file:Cliet Class Diagram}
        \item ClientClassDiagram.png
        \subitem The class diagram describing our classes and their metadata. 
    \end{file}
    
    \begin{file}
        \label{attachment:file:EchoClientClient jar}
        \item EchoClientClient.jar
        \subitem The client we have used for our testing.
    \end{file}
    
    \begin{file}
        \label{attachment:file:Client config}
        \item Client.config
        \subitem An example configuration for the Echo client.
    \end{file}
    
    \begin{file}
        \label{attachment:file:TestClient java}
        \item TestClient.java
        \subitem The source code for the Echo client.
    \end{file}
    
    \begin{file}
        \label{attachment:file:EchoServiceLargeReply.war}
        \item EchoServiceLargeReply.war
        \subitem A simple service which echoes responses back and pads them with 10Kb of text.
    \end{file}
    
    \begin{file}
        \label{attachment:file:hc.diff}
        \item hc.diff
        \subitem A diff file which can be applied to the HTTPCore source to apply the changes for DiffServ support.
    \end{file}
    
    \begin{file}
        \label{attachment:file:no.ntnu.qos.jar}
        \item no.ntnu.qos.jar
        \subitem The server side, neatly packed into a jar ready for deployment in an ESB near you.
    \end{file}
    
    \begin{file}
        \label{attachment:file:synapse-configs.zip}
        \item synapse-configs.zip
        \subitem The commented Synapse configuration files, the values may not be correct, but the comments are.
    \end{file}
    
    \begin{file}
        \label{attachment:file:mediator-configuration.zip}
        \item mediator-configuration.zip
        \subitem The necessary configuration files for the ESB using our test setup.
    \end{file}
    
    \begin{file}
        \label{attachment:file:Test Case 1}
        \item Test-Case-1.tar.gz
        \subitem Necessary files for Test Case 1.
    \end{file}
    
    \begin{file}
        \label{attachment:file:Test Case 2}
        \item Test-Case-2.tar.gz
        \subitem Necessary files for Test Case 2.
    \end{file}
    
    \begin{file}
        \label{attachment:file:Test Case 3}
        \item Test-Case-3.tar.gz
        \subitem Necessary files for Test Case 3.
    \end{file}
    
    \begin{file}
        \label{attachment:file:Test Case 4}
        \item Test-Case-4.tar.gz
        \subitem Necessary files for Test Case 4.
    \end{file}
    
    \begin{file}
        \label{attachment:file:Test Case 5}
        \item Test-Case-5.tar.gz
        \subitem Necessary files for Test Case 5.
    \end{file}
    
    \begin{file}
        \label{attachment:file:Test Case 6}
        \item Test-Case-6.tar.gz
        \subitem Necessary files for Test Case 6.
    \end{file}
    
\end{itemize}
    
    
